### 2024-09-20 manuscript/manuscript.qmd
update methods
add additional detail to method, including quality control subsection

The initial search yielded 553 potential studies, which were interactively screened for relevance in three stages by both authors, resulting in 46 studies that passed our inclusion criteria (define here: has included some form of emotion modelling with a set of features, and outcome measures such as $R^2$ or classification accuracy ($F1$ score or *precision* or *recall*) and overall quality control; see [SI](http://) for a breakdown). After the screening stage, we define a set of entities to extract characterising music (genre, stimulus number \[N\], duration), features extracted (number, type, source, defined by [@panda2020audio]), model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), model complexity (??? model architecture?), and type of model cross-validation. We converted all regression results into $R^2$ values for valence and arousal and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].

@@

-   Devote some sentences to quality control issues (what were the most common reasons for eliminating studies).

>>>>

The initial search yielded 553 potential studies after excluding duplicate entries. We interactively screened them for relevance in three stages, resulting in 46 studies that passed our inclusion criteria (music emotion studies using classification or regression methods to predict emotion ratings of music using symbolic or audio features, and containing sufficient detail to convert results to $R^2$ or $MCC$ values see [SI](http://) for a breakdown). After the screening stage, we defined a set of entities to extract characterising (i) music (genre, stimulus number \[N\], duration), (ii) features extracted (number, type, source, defined by [@panda2020audio]), (iii) model type (regression, neural network, SVM, etc.) and outcome measure ($R^2$, *MSE*, *MCC*), (iv) model complexity (i.e., approximate number of features used to predict ratings), and (v) type of model cross-validation. We converted all regression results into $R^2$ values for valence and arousal and classification results into Matthews correlation coefficient [*MCC*, @chicco2020advantages].

@@

## Quality Control

The search yielded studies of variable (and occasionally questionable) quality. To mitigate potentially spurious effects resulting from the inclusion of low-quality studies, [we excluded studies lacking sufficient details about stimuli, analyzed features, or model architecture](include approx # for each?). Additionally, we excluded results comprising algorithms trained on image features such as spectrograms (affecting two studies, one of which was eliminated).Finally, we excluded one study published in two journals of questionable relevance to MER. This includes *Mathematical Problems in Engineering* which ceased publication following a large number of retractions in September 2024.
